Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-03-30 paper/paper-nature_format.tex
paper updates

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{February 28, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a key tenet of
democracy, and a critical resource for political science research. In
Australia, following the British tradition, the written record of what
is said in parliament is known as Hansard. While the Australian Hansard
has always been publicly available, it has been difficult to use it for
the purpose of large-scale macro and micro-level text analysis because
it has not been available as a dataset of sufficient quality. Following
the lead of the Linked Parliamentary Data project which achieved this
for Canada, we provide a new, comprehensive, high-quality database that
captures all proceedings of the Australian parliamentary debates from
1998 to the present using Hansard. The database is publicly available
and can be readily linked to other datasets such as election results.
The creation and accessibility of this database will enable the
exploration of questions that are not currently possible to explore,
serving as a valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, enhanced, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in a number of Commonwealth countries such as
Canada, the United Kingdom, and Australia (Vice and Farrell 2017). Given
the content and magnitude of these records, they have significance,
particularly in the context of political science research. In the case
of Canada, a team of researchers at the University of Toronto have
digitized Hansard from 1901 to 2019, an endeavour called the Linked
Parliamentary Data (LiPaD) project (Beelen et al. 2017). Having a
digitized version of Hansard enables researchers to perform advanced
analyses on these records using text analysis tools and statistical
modelling. Following the lead of the LiPaD project, in this paper we
introduce a novel database for the Australian Hansard. This is composed
of individual datasets for each sitting day in the House of
Representatives from 1998 to 2022, containing details on everything said
in parliament in a form which can be readily used by researchers. With
the development of tools for large-scale text analysis, this database
will serve as a valuable resource for efficiently studying and exploring
political behaviour in Australia over time.

The House of Representatives performs a number of crucial governmental
functions, such as creating new laws and overseeing government
expenditure (House of Representatives 2018, ch.~1). The House operates
under a parallel chamber setup, meaning there are two debate venues
where proceedings take place: the Chamber, and the Federation Chamber.
Sittings of the House follow a predefined order of business, regulated
by procedural rules called standing orders (House of Representatives
2018, ch.~8). A typical sitting day in the Chamber has a number of
scheduled proceedings including debates on government business, 90
second member statements, and Question Time (House of Representatives
2018, ch.~8). The Federation Chamber was created in 1994 as a
subordinate debate venue of the Chamber. This allows for better time
management of House business as its proceedings occur simultaneously
with those of the Chamber (House of Representatives 2018, ch.~21).
Sittings in the Federation Chamber are quite different to those of the
Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members (House of Representatives 2018, ch.~21). It is the recording and
compilation of all of these proceedings on which Hansard is based, and
it is essentially, but not entirely, verbatim.

A week or so after each sitting day, a transcript is available for
download from the official Parliament of Australia website in both
static PDF and extensible markup language (XML) form. The PDF is the
official release, which is converted to typed text using Optical
Character Recognition (OCR) technology (Sherratt 2016). This conversion
allows for the production of the XML formatted transcript, though these
are not always perfect conversions and are particularly flawed in the
early decades of Hansard (Sherratt 2016). The PDF imposes formatting
designed for humans to read with ease, whereas XML is designed for
consistency and machine legibility. The nature of XML enables us to more
easily use code to manipulate these records at scale, motivating our
choice to develop our database solely using the XML formatted files. In
cases where we were unsure on how to proceed with processing the XML, we
defer first to the PDF, and then to the video recording of the
proceeding if available.

At present, the Hansard format that is available on the Parliament of
Australia website is not accessible for large scale analysis. To this
point, various researchers have had to create their own databases in an
attempt to produce usable, complete data based on content from the
Australian Parliament website. For instance, Sherratt (2016) created an
online, easy to read database of Hansard from 1901 to 1980 using the XML
files. These data can be navigated by year, parliament, people, and
bills (Sherratt 2016). In an effort to make the Australian Parliamentary
Handbook more accessible, Leslie (2021) has released an \texttt{R}
package which includes data on all Members of the Australian House of
Representatives from 1945 to 2019. Further, Alexander and Hodgetts
(2021) created the \texttt{AustralianPoliticians} \texttt{R} package,
which contains a number of datasets related to the political and
biographical information of Australian federal politicians who were
active between 1901 and 2021.

A number of papers exist which utilize components of Australian Hansard
to explore various research topics. For example, Salisbury (2011) used
online Hansard records to investigate the occurrences of unparliamentary
comments by members of the House, where The Speaker tells that member to
withdraw their remark. Rasiah (2010) worked with Question Time data from
Hansard transcripts during February and March of 2003, to investigate
resistance of politicians in answering questions about Iraq. In their
work, Fraussen, Graham, and Halpin (2018) use Hansard to quantify
political prominence by investigating strategic mentions of interest
groups by elected officials. Finally, the work of Alexander and
Alexander (2021) offers a dataset of the Australian Hansard, along with
an analysis of the effect of elections and changes in Prime Ministers
upon topics mentioned in parliament. Alexander and Alexander (2021)
created this database with the static PDF versions of Hansard, using OCR
to digitize these files into text which is suitable for analysis. This
means there are considerable digitization errors especially in the first
half of the dataset.

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child-nodes,
where the first child-node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. Note that the Federation Chamber does not meet on
every sitting day, so this child element is not present in every XML
file. The use of separate child nodes allows for the distinction of
proceedings of the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with a business start which is
followed by a series of debates. Debate nodes can contain a sub-debate 1
child-node which has a sub-debate 2 child-node nested within it. That
said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of
these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the speaker and the time of their first statement.
Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate
settings --- they are often composed of a series of interjections and
continuations. These statements are categorized under different
sub-nodes depending on their nature, such as
\texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will follow in Section~\ref{sec-qa}.

Figure~\ref{fig-xml1} provides an example of the beginning of an XML
file for Hansard, which illustrates the structure outlined in the nested
list above. As stated, the XML structure begins with a parent element
\texttt{"hansard"} (highlighted in blue), followed by a child element
\texttt{"session.header"} (highlighted in yellow) with sub-child
elements such as the date and parliament number, which are all
highlighted in pink. Next there is the child element containing
everything that takes place in the Chamber, \texttt{"chamber.xscript"},
which is also highlighted in yellow in Figure~\ref{fig-xml1}. As
previously mentioned, the first sub-node of \texttt{"chamber.xscript"}
is the business start. The structure of the business start can be seen
between the nodes highlighted in green in Figure~\ref{fig-xml1}, where
the content we parse from the business start are highlighted in orange.

\textbf{does this feel a bit repetitive? do you think it's worth
keeping?}

@@

\caption{\label{fig-xml1}Snapshot of beginning of XML file for Hansard
on 25 February 2020}

@@

Evidently, the nature of XML formatting means that different pieces of
information are categorized under a series of uniquely named and nested
nodes. As a result, to parse each piece of information, one must specify
the unique hierarchy of nodes in which it is structured. This is known
as an XPath expression, and tells the parser how to navigate the XML
document to obtain the desired information. For example, the session
header date in Figure~\ref{fig-xml1} can be accessed using the XPath
expression ``\texttt{hansard/session.header/date}''. We began our first
script by parsing every piece of information contained in the XML
document, using these unique XPath expressions to do so.

The next step was to further develop our script to produce tidy data
sets containing each parsed element, where each statement is separated
onto its own row with details about the speaker, and rows are placed in
chronological order. This first involved correcting the variable classes
and adding a number of indicator variables to differentiate where
statements came from, such as Chamber versus Federation Chamber or
sub-debate 1 versus sub-debate 2. The next key task stemmed from the
fact that the raw text data were not separated by each statement when
parsed. In other words, any interjections, comments made by The Speaker
or Deputy Speaker and continuations within an individual speech were all
parsed together as a single string. As such, the name, name ID,
electorate and party details were only provided for the person whose
turn it was to speak. Splitting up these speeches in a way which would
be generalizable across sitting days required much thought and effort.
Section~\ref{sec-interject} will provide further details on the
intricacies of this task.

Since we are looking at a wide time span of documents, there are
expectedly a number of changes in the way they are formatted over time.
These became apparent as we ran our script on XML files from earlier
sitting days. Some changes are as subtle as a differently named
child-node, while others are as extensive as a completely different
nesting structure. Smaller changes were accounted for as we became aware
of them, and embedded into the code in a way that would not cause issues
for parsing more current Hansards with subtle differences in formatting.
However, as mentioned, more significant changes in the XML structure of
Hansard are what necessitated the development of separate scripts as we
worked backwards in time. Further, while working backward in time, it
became clear that not every sitting day contains every possible XML
element. For example, some days did not have sub-debate 2 content, and
some days did not have a Federation Chamber proceeding. To improve the
generalizability of these scripts, if-else statements were embedded
within the code wherever an error might arise due to a missing element.
For example, the entire Federation Chamber block of code is wrapped in
an if-else statement for each script, so that it only executes if what
the code attempts to parse actually exists in the file.

@@

While the modifications needed to develop the second script were quite
straightforward, this was not the case for our next script. The typical
tree structure of Hansard XMLs spanning from 1998 to March 2011 has an
important difference from that of XMLs released after March 2011,
necessitating many changes to be made in our methodology. In XMLs after
March 2011, which our first two scripts successfully parse, the first
two child-nodes of \texttt{\textless{}speech\textgreater{}} are
typically \texttt{\textless{}talk.start\textgreater{}}, and
\texttt{\textless{}talk.text\textgreater{}}. The first child-node
contains data on the person whose turn it is to speak, and the second
contains the entire contents of that speech --- including all
interjections, comments and continuations. After the
\texttt{\textless{}talk.text\textgreater{}} element closes, there are
typically a series of other child-nodes which provide a skeleton
structure for how the speech proceedings went in chronological order.
For example, if the speech began, was interrupted by one member, and
then continued uninterrupted until the end, there would be one
\texttt{\textless{}interjection\textgreater{}} node and one
\texttt{\textless{}continuation\textgreater{}} node following the
\texttt{\textless{}talk.text\textgreater{}} node. These would contain
details on the person who made each statement such as their party and
electorate.

In contrast, the speech contents in XMLs from 1998 up to and including
24 March 2011 are nested differently --- there is no
\texttt{\textless{}talk.text\textgreater{}} node. Rather than this
single child-node that contains all speech content, statements are
categorized in individual child-nodes. This means that unlike our code
for parsing more current Hansards, we cannot specify a single XPath
expression such as ``\texttt{debate/speech/talk.text}'' or
``\texttt{debate/subdebate.1/speech/talk.text}'' to extract all
speeches, in their entirety, at once. This difference in nesting
structure made our second script unusable for parsing transcripts
preceding 10 May 2011, and required us to change our data processing
approach considerably.

Since there are numerous speeches in a typical Hansard, each having
multiple child-nodes with the same names
(i.e.~\texttt{\textless{}continuation\textgreater{}},
\texttt{\textless{}interjection\textgreater{}}), it is difficult to
parse everything while maintaining the correct ordering of statements.
We found that the most straightforward way to preserve the ordering of
statements and to parse all speech contents at once was to parse from
the \texttt{\textless{}debate\textgreater{}} element directly. The
reason we did not use its \texttt{\textless{}speech\textgreater{}}
child-node is because every speech has a unique structure of node
children, and this makes it difficult to write code for data cleaning
which is generalizable across all speeches and sitting days.

The challenge with parsing through the
\texttt{\textless{}debate\textgreater{}} element is that every piece of
data stored in that element is parsed as a single string, including all
\texttt{\textless{}talk.start\textgreater{}} data, and all nested
sub-debate data. For example, the data shown in
Figure~\ref{fig-patternEX} would be parsed as a single string preceding
the speech content, like so:

@@

This was not isolated to just the beginning of speeches --- details on
individuals interjecting or commenting during speeches were also
captured this way. To separate statements out correctly, we collected
all of these patterns using the
\texttt{\textless{}talk.start\textgreater{}} node, and used them to
split statements wherever one of these patterns was found. After
separating statements, we were later able remove these patterns from the
body of text. We also used this method of extracting and later removing
unwanted patterns for other pieces of data which did not belong to the
debate proceedings, such as sub-debate titles.

Once we finalized this new method of processing the data, we proceeded
with data cleaning using the same general approach as in the first two
scripts to produce the same structure of CSV output. We then worked
backwards in time and modified the code as needed for generalizability.
Throughout this process we found a number of transcription errors
present in the XMLs from earlier years. We fixed these manually,
deferring to the official release to ensure the correct information was
filled in. Since there were a number of transcription errors specific to
the 2000s, we chose to create a fourth script for parsing 1998 and 1999.
This allowed us to remove all the code which was needed to resolve
specific transcription errors of the 2000s, to avoid an overly long
script and in turn improving computational efficiency. As such, our
fourth script is essentially the same as the third, the only difference
being that it has code specific to fixing transcription errors from 1998
and 1999.

@@

A key characteristic of the Australian parliament system is the ability
for the executive government to be held accountable for their decisions.
One core mechanism by which this is achieved is called Question Time.
This is a period on each sitting day in the Chamber where members of the
House can ask ministers two types of questions: questions in writing
which are written in advance, or questions without notice which are
asked verbally in the Chamber and are responded to in real time (House
of Representatives 2021). Parsing the components of Question Time
required a slightly different approach than that of the debate speech,
because of its unique structure in the XML document. Questions without
notice are included directly in the \texttt{"chamber.xscript"} child
node, with sub-child nodes called \texttt{"question"} and
\texttt{"answer"} to differentiate the two. Questions in writing,
however, are embedded in their own child node called
\texttt{"answers.to.questions"} at the end of the XML file.

To parse questions without notice and questions in writing in the first
two scripts, we extracted all question and answer elements from the
\texttt{"chamber.xscript"} and \texttt{"answers.to.questions"} child
nodes. For the third and fourth scripts, our method of parsing the
\texttt{"chamber.xscript"} speeches meant that all questions without
notice content was already parsed in order. Similar to the rest of the
speech content, we used those patterns of data preceding the text to
separate questions and answers. Finally, since questions in writing
exist in their own child node we were able to use the same parsing
method for the third and fourth scripts as we did for the first and
second scripts.

We then added binary flags to differentiate between questions and
answers, determined by which sub-child node the statement was extracted
from, that is, whether it came from a
\texttt{\textless{}question\textgreater{}} node, or an
\texttt{\textless{}answer\textgreater{}} node. Sometimes, questions were
incorrectly transcribed under an answer node and vice-versa, in which
cases we manually corrected the question and answer flags using the
\texttt{str\_detect} function from the \texttt{stringr} package. For
instance, our code for parsing questions searches for any statements
which include ``has provided the following answer to the honourable
member's question'', in which case we re-code that statement as an
answer. Once all questions and answers were correctly classified as
such, we could then merge all the content back together such that each
question was followed by its associated answer. This was straightforward
due to the fact that by nature of XML parsing, all questions and answers
were parsed in the order in which they appeared in the transcript.

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{March 30, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro and micro-level text analysis because it has only been
available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures all
proceedings of the Australian parliamentary debates from 1998 to the
present using Hansard. The database is publicly available and can be
linked to other datasets such as election results. The creation and
accessibility of this database enables the exploration of questions that
have not been possible to explore, serving as a valuable resource for
both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in many Commonwealth countries such as Canada,
the United Kingdom, and Australia (Vice and Farrell 2017). Given the
content and magnitude of these records, they have significance,
particularly in the context of political science research. In the case
of Canada, the Hansard has been digitized for 1901 to 2019 (Beelen et
al. 2017). Having a digitized version of Hansard enables researchers to
perform advanced analyses on these records using text analysis tools and
statistical modelling. Following the lead of that project, in this paper
we introduce a novel database for the Australian Hansard. This is
composed of individual datasets for each sitting day in the House of
Representatives from 1998 to 2022, containing details on everything said
in parliament in a form that can be readily used by researchers. With
the development of tools for large-scale text analysis, this database
will serve as a valuable resource for efficiently studying and exploring
political behaviour in Australia over time.

The Australian House of Representatives performs a number of crucial
governmental functions, such as creating new laws and overseeing
government expenditure (House of Representatives 2018, ch.~1). The House
operates under a parallel chamber setup, meaning there are two debate
venues where proceedings take place: the Chamber, and the Federation
Chamber. Sittings of the House follow a predefined order of business,
regulated by procedural rules called standing orders (House of
Representatives 2018, ch.~8). A typical sitting day in the Chamber has a
number of scheduled proceedings including debates on government
business, 90 second member statements, and Question Time (House of
Representatives 2018, ch.~8). The Federation Chamber was created in 1994
as a subordinate debate venue of the Chamber. This allows for better
time management of House business as its proceedings occur
simultaneously with those of the Chamber (House of Representatives 2018,
ch.~21). Sittings in the Federation Chamber are quite different to those
of the Chamber in terms of their order of business and scope of
discussion. Business matters discussed in the Federation Chamber are
limited largely to intermediate stages of bill development, and the
business of private Members (House of Representatives 2018, ch.~21). It
is the recording and compilation of all of these proceedings on which
Hansard is based, and it is essentially, but not entirely, verbatim.

A week or so after each sitting day, a transcript is available for
download from the official Parliament of Australia website in both PDF
and extensible markup language (XML) form. The PDF is the official
release. For early decades there is a need to digitize PDFs using
Optical Character Recognition (OCR) technology and there are many flaws
(Sherratt 2016). The PDF imposes formatting designed for humans to read
with ease, whereas XML is designed for consistency and machine
legibility. The nature of XML enables us to more easily use code to
manipulate these records at scale, motivating our choice to develop our
database solely using the XML formatted files. In cases where we were
unsure on how to proceed with processing the XML, we defer first to the
PDF, and then to the video recording of the proceeding, if available.

At present, the Hansard format that is available on the Parliament of
Australia website is not accessible for large scale analysis. To this
point, various researchers have had to create their own databases of
usable, complete data based on content from the Australian Parliament
website. For instance, Sherratt (2016) created an online, easy to read
database of Hansard from 1901 to 1980 using the XML files. These data
can be navigated by year, parliament, people, and bills (Sherratt 2016).
To make the Australian Parliamentary Handbook more accessible, Leslie
(2021) has released an \texttt{R} package which includes data on all
Members of the Australian House of Representatives from 1945 to 2019.
Further, Alexander and Hodgetts (2021) created the
\texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, Salisbury (2011) used online
Hansard records to investigate the occurrences of unparliamentary
comments by members of the House, where the Speaker tells that member to
withdraw their remark. Rasiah (2010) worked with Question Time data from
Hansard transcripts during February and March of 2003, to investigate
resistance of politicians in answering questions about Iraq. In their
work, Fraussen, Graham, and Halpin (2018) use Hansard to quantify
political prominence by investigating strategic mentions of interest
groups by elected officials. Finally, the work of Alexander and
Alexander (2021) offers a dataset of the Australian Hansard, along with
an analysis of the effect of elections and changes in Prime Ministers
upon topics mentioned in parliament. Alexander and Alexander (2021)
created this database with the static PDF versions of Hansard, using OCR
to digitize these files into text which is suitable for analysis. This
means there are considerable digitization errors especially in the first
half of the dataset.

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child-nodes,
where the first child-node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. Note that the Federation Chamber does not meet on
every sitting day, so this child element is not present in every XML
file. The use of separate child nodes allows for the distinction of
proceedings of the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with a business start which is
followed by a series of debates. Debate nodes can contain a
\texttt{\textless{}subdebate.1\textgreater{}} child-node which has a
\texttt{\textless{}subdebate.2\textgreater{}} child-node nested within
it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the speaker and the time of their first statement.
Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate
settings --- they are often composed of a series of interjections and
continuations. These statements are categorized under different
sub-nodes depending on their nature, such as
\texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will follow in Section~\ref{sec-qa}.

Figure~\ref{fig-xml1} provides an example of the beginning of an XML
file for Hansard, which illustrates the structure outlined in the nested
list above. As stated, the XML structure begins with a parent element
\texttt{\textless{}hansard\textgreater{}} (highlighted in blue),
followed by a child element
\texttt{\textless{}session.header\textgreater{}} (highlighted in yellow)
with sub-child elements such as the date and parliament number, which
are all highlighted in pink. Next there is the child element containing
everything that takes place in the Chamber,
\texttt{\textless{}chamber.xscript\textgreater{}}, which is also
highlighted in yellow in Figure~\ref{fig-xml1}. As previously mentioned,
the first sub-node of \texttt{\textless{}chamber.xscript\textgreater{}}
is the business start. The structure of the business start can be seen
between the nodes highlighted in green in Figure~\ref{fig-xml1}, where
the content we parse from the business start is highlighted in orange.

@@

\caption{\label{fig-xml1}Snapshot of the beginning of the XML file for
Hansard on 25 February 2020}

@@

Evidently, the nature of XML formatting means that different pieces of
information are categorized under a series of uniquely named and nested
nodes. As a result, to parse each piece of information, one must specify
the unique hierarchy of nodes in which it is structured. This is known
as an XPath expression, and tells the parser how to navigate the XML
document to obtain the desired information. For example, the session
header date in Figure~\ref{fig-xml1} can be accessed using the XPath
expression ``\texttt{hansard/session.header/date}''. When specifying an
XPath expression, one can use an ``or'' operator to obtain elements from
multiple node paths at once, in the order that they appear in the
document. We did so throughout our script as we parsed uniquely nested
speech content, as it allows for the correct ordering of elements to be
maintained. We began our first script by parsing all the business start,
speech text, and Question Time contents contained in the XML document,
using these unique XPath expressions to do so. Hansard records contain a
number of statements throughout that were not explicitly spoken in
parliament. For example, the text in Figure~\ref{fig-content_ex} beneath
the bold subtitle ``Report from Federation Chamber'' is not attributed
to a particular member and was not spoken aloud during the parliamentary
proceedings. In contrast, the text which comes afterward was spoken
aloud in parliament by The Speaker at 14:01. Generally, unspoken text is
nested under \texttt{\textless{}debate.text\textgreater{}} or
\texttt{\textless{}subdebate.text\textgreater{}} nodes, while spoken
text is categorized under \texttt{\textless{}speech\textgreater{}}.
Importantly, in our work we focus primarily on parsing spoken speech
content (i.e.~what is nested within
\texttt{\textless{}speech\textgreater{}} nodes), such as what is stated
by The Speaker in Figure~\ref{fig-content_ex}. For this reason, many
Hansard transcriptions which are not spoken text may not be captured in
our database. In future work, capturing this unspoken content in our
database would be a priority.

{\centering \includegraphics[width=1.88542in,height=\textheight]{images/content_ex.png}

\caption{\label{fig-content_ex}Snapshot from page 7129 of the PDF file
for Hansard on 26 March 2013}

The next step was to further develop our script to produce tidy data
sets containing all parsed text elements, where each statement is
separated onto its own row with details about the speaker, and rows are
maintained in chronological order. This first involved correcting the
variable classes and adding several indicator variables to differentiate
where statements came from, such as Chamber versus Federation Chamber or
sub-debate 1 versus sub-debate 2. The next key task stemmed from the
fact that the raw text data were not separated by each statement when
parsed. In other words, any interjections, comments made by The Speaker
or Deputy Speaker and continuations within an individual speech were all
parsed together as a single string. As such, the name, name ID,
electorate and party details were only provided for the person whose
turn it was to speak. Splitting up these speeches in a way which would
be generalizable across sitting days required much thought and effort.
Section~\ref{sec-interject} will provide further details on the
intricacies of this task.

Since we are looking at a wide time span of documents, there are many
changes in the way they are formatted over time. These became apparent
as we ran our script on XML files from earlier sitting days. Some
changes are as subtle as a differently named child-node, while others
are as extensive as a completely different nesting structure. Smaller
changes were accounted for as we became aware of them, and embedded into
the code in a way that would not cause issues for parsing more current
Hansards with subtle differences in formatting. However, as mentioned,
more significant changes in the XML structure of Hansard are what
necessitated the development of separate scripts as we worked backwards
in time. Further, while working backward in time, it became clear that
not every sitting day contains every possible XML element. For example,
some days did not have sub-debate 2 content, and some days did not have
a Federation Chamber proceeding. To improve the generalizability of
these scripts, if-else statements were embedded within the code wherever
an error might arise due to a missing element. For example, the entire
Federation Chamber block of code is wrapped in an if-else statement for
each script, so that it only executes if what the code attempts to parse
exists in the file.

@@

While the modifications needed to develop the second script were quite
straightforward, this was not the case for our next script. The typical
tree structure of Hansard XMLs spanning from 1998 to March 2011 has an
important difference from that of XMLs released after March 2011,
necessitating many changes to be made in our methodology. In XMLs after
March 2011, which our first two scripts successfully parse, the first
two child-nodes of \texttt{\textless{}speech\textgreater{}} are
typically \texttt{\textless{}talk.start\textgreater{}}, and
\texttt{\textless{}talk.text\textgreater{}}. The first child-node
contains data on the person whose turn it is to speak, and the second
contains the entire contents of that speech --- including all
interjections, comments, and continuations. After the
\texttt{\textless{}talk.text\textgreater{}} element closes, there are
typically a series of other child-nodes which provide a skeleton
structure for how the speech proceedings went in chronological order.
For example, if the speech began, was interrupted by one member, and
then continued uninterrupted until the end, there would be one
\texttt{\textless{}interjection\textgreater{}} node and one
\texttt{\textless{}continuation\textgreater{}} node following the
\texttt{\textless{}talk.text\textgreater{}} node. These would contain
details on the person who made each statement such as their party and
electorate.

In contrast, the speech contents in XMLs from 1998 up to and including
24 March 2011 are nested differently --- there is no
\texttt{\textless{}talk.text\textgreater{}} node. Rather than this
single child-node that contains all speech content, statements are
categorized in individual child-nodes. This means that unlike our code
for parsing more current Hansards, we cannot specify a single XPath
expression such as
``\texttt{chamber.xscript//debate//speech/talk.text}'' to extract all
speeches, in their entirety, at once. This difference in nesting
structure made many components of our second script unusable for
processing transcripts preceding 10 May 2011, and required us to change
our data processing approach considerably.

Since the earlier Hansard XMLs do not have a
\texttt{\textless{}talk.text\textgreater{}} node, we found that the most
straightforward way to preserve the ordering of statements and to parse
all speech contents at once was to parse from the
\texttt{\textless{}debate\textgreater{}} element directly. The reason we
did not use its \texttt{\textless{}speech\textgreater{}} child-node is
because every speech has a unique structure of node children, and this
makes it difficult to write code for data cleaning which is
generalizable across all speeches and sitting days. The challenge with
parsing through the \texttt{\textless{}debate\textgreater{}} element is
that every piece of data stored in that element is parsed as a single
string, including all \texttt{\textless{}talk.start\textgreater{}} data,
and all nested sub-debate data. For example, the data shown in
Figure~\ref{fig-patternEX} would be parsed as a single string preceding
the speech content, like so:

@@

This was not isolated to just the beginning of speeches --- details on
individuals interjecting or commenting during speeches were also
captured this way. To separate statements out correctly, we collected
all of these patterns using the
\texttt{\textless{}talk.start\textgreater{}} node, and used them to
split statements wherever one of these patterns was found. After
separating the statements, we were able to remove these patterns from
the body of text. We also used this method of extracting and later
removing unwanted patterns for other pieces of data which did not belong
to the debate proceedings, such as sub-debate titles.

Once we finalized this new method of processing the data, we proceeded
with data cleaning using the same general approach as in the first two
scripts to produce the same structure of CSV output. We then worked
backwards in time and modified the code as needed for generalizability.
Throughout this process we found many transcription errors present in
the XMLs from earlier years. We fixed these manually, deferring to the
official release to ensure the correct information was filled in. Since
there were a number of transcription errors specific to the 2000s, we
chose to create a fourth script for parsing 1998 and 1999. This allowed
us to remove all the code which was needed to resolve specific
transcription errors of the 2000s, to avoid an overly long script and in
turn improving computational efficiency. As such, our fourth script is
essentially the same as the third, with the only difference being that
it has code specific to fixing transcription errors from 1998 and 1999.

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
members of the House can ask ministers two types of questions: questions
in writing which are written in advance, or questions without notice
which are asked verbally in the Chamber and are responded to in real
time (House of Representatives 2021). Questions without notice are
included directly in the \texttt{"chamber.xscript"} child node, with
sub-child nodes called \texttt{"question"} and \texttt{"answer"} to
differentiate the two. Questions in writing, however, are embedded in
their own child node called \texttt{"answers.to.questions"} at the end
of the XML file.

Our approach to parse the \texttt{"chamber.xscript"} speeches used in
all four scripts meant that all questions without notice content was
already parsed in order. For the first two scripts, questions and
answers were already separated onto their own rows. For the third and
fourth scripts, just as we did with the rest of the speech content, we
used those patterns of data preceding the text to separate questions and
answers. Finally, since questions in writing exist in their own child
node we were able to use the same parsing method for all scripts, which
was simply to extract all question and answer elements from the
\texttt{"answers.to.questions"} child node.

We then added binary flags to differentiate between questions and
answers. To do this in the first and second scripts, we separately
re-parsed question and answer content using the XPath expressions
\texttt{"chamber.xscript//question"} and
\texttt{"chamber.xscript//answer"}, added the correct question and
answer flags accordingly, and then added those flags back to the main
dataframe based on exact text matches. For the third and fourth scripts,
we made use of the fact that the patterns preceding text transcribed
under a question node were stored separately from those transcribed
under an answer node. As a result, we could readily use those patterns
to flag questions and answers correctly based on which list of patterns
it belonged to. Sometimes, questions were incorrectly transcribed under
an answer node and vice-versa, in which cases we manually corrected the
question and answer flags using the \texttt{str\_detect} function from
the \texttt{stringr} package. For instance, we check for any statements
flagged as questions which include the phrase ``has provided the
following answer to the honourable member's question'', in which case we
re-code that statement as an answer.

The next step was to merge Question Time contents with all the debate
speech. Doing so with the questions without notice content was
straightforward. As mentioned, our method of parsing meant that
everything was already parsed together in order, so we did not have to
perform any additional merging. For questions in writing, merging this
content was also straightforward due to the fact that it is always at
the very end of Hansard. This means that we could simply bind question
in writing rows to the bottom of the main dataframe. This approach was
used for all four scripts.
